% 00_abstract.tex — converted from content/book.md, "Abstract" (Stage 9.3).

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Generating high-quality, structured technical documents --- particularly books
typeset with \LaTeX{} --- usually demands substantial manual effort,
specialised knowledge, and careful attention to detail. The process is
time-consuming, error-prone, and hard to scale. In this project we explore a
multi-agent pipeline built on the CrewAI framework that aims to automate much
of this work for \LaTeX{} book generation.

Our approach orchestrates a small crew of specialised agents, each with a
distinct role: planning the outline, writing the draft, reviewing it, and
curating references. The agents run sequentially, and the output of one
becomes context for the next. The goal is to turn a high-level topic into
structured, compilation-ready content.

This report describes the architecture, the implementation, and our honest
experience moving from an early proof-of-concept toward something closer to
production. We report the measured cost of one real content-generation run
against the Gemini model \path{gemini/gemini-2.5-flash}, and we are
deliberately careful to separate measured results from proposed future
evaluation. We do not claim the system is already fully production-ready: the
resulting \LaTeX{} article was assembled, compiled, and validated as part of
this assignment, while the broader system is still presented as a
proof-of-concept rather than a production-ready service.
