% 01_introduction.tex — converted from content/book.md, "1. Introduction"
% (Stage 9.3).

\chapter{Introduction}

Technical communication increasingly demands efficiency, accuracy, and
scalability. From academic papers to software manuals, the need to produce
high-quality structured documents is constant. This chapter sets the context
by outlining the challenges in current document-generation practice and the
potential of multi-agent systems to address them.

\section{The Challenge of Automated Document Generation}

Creating structured documents for academic or professional publishing is
complex. \LaTeX{} offers excellent control over typography, layout, and
cross-referencing, but it has a steep learning curve and strict syntax.
Writing a book-length \LaTeX{} document by hand involves many iterative
steps: planning, research, drafting, formatting, keeping chapters consistent,
managing bibliographies, producing figures and tables, and proofreading. Each
step is labour-intensive and easy to get wrong, and scaling the work across
multiple documents or frequent updates quickly becomes a bottleneck. The real
difficulty is not just generating text, but generating \emph{structured,
valid, semantically correct} text within a specific technical format.

\section{The Promise of Multi-Agent Systems in AI}

Recent advances in large language models (LLMs) and multi-agent frameworks
offer a way to address these limitations. A multi-agent system uses several
specialised agents, each with its own role and tools, that collaborate to
reach a goal that is hard for a single monolithic model. By breaking a large
task into smaller pieces and assigning them to focused agents, these systems
mimic a human collaborative workflow. This modularity makes the process
easier to reason about and refine, and it is a natural fit for multi-step
work such as planning, writing, reviewing, and reference curation.

\section{Project Scope and Objectives}

This project designs, implements, and evaluates a CrewAI-based multi-agent
pipeline for generating a \LaTeX{} book. Our objectives are:

\begin{itemize}
  \item \textbf{Design:} define the agent roles and the task flow for book
        generation.
  \item \textbf{Implement:} build the offline-by-default runner, the
        deterministic validation layer, and a real run path that is
        explicitly gated.
  \item \textbf{Generate:} produce structured content for the article from a
        high-level topic.
  \item \textbf{Evaluate:} record the measured cost of a real run and propose
        (without fabricating) the metrics we would use for a fuller
        evaluation.
  \item \textbf{Production readiness:} discuss honestly what a transition
        from proof-of-concept to a maintainable, deployable system would
        require.
\end{itemize}

The anticipated benefits are reduced manual effort, more consistent
structure, and faster drafting cycles --- while keeping a clear separation
between the agentic (LLM) layer and the deterministic build/validation
layer.
