% 02_background.tex — converted from content/book.md, "2. Background and
% Related Work" (Stage 9.3). Citations mirror the [n] markers in the cleaned
% Markdown.

\chapter{Background and Related Work}

\section{Understanding CrewAI and Multi-Agent Orchestration}

CrewAI is an open-source framework for building and managing multi-agent
systems~\cite{crewai_docs}. The underlying idea --- decomposing a problem
across several cooperating agents instead of one monolithic solver --- is
well established in the AI literature~\cite{wooldridge2009mas,
russell2020aima}. CrewAI's core components are:

\begin{itemize}
  \item \textbf{Agents:} autonomous entities with a role, goal, backstory,
        and an attached LLM, optionally equipped with tools.
  \item \textbf{Tasks:} units of work assigned to agents, defining the
        objective, context, and expected output; tasks can be chained so one
        output feeds the next.
  \item \textbf{Tools:} external functions agents can call (web search, file
        I/O, custom validation scripts).
  \item \textbf{Processes:} how agents collaborate --- a \texttt{sequential}
        process runs tasks one after another, while a \texttt{hierarchical}
        process lets a manager agent delegate.
  \item \textbf{Crews:} a collection of agents, tasks, and a process working
        toward one objective.
\end{itemize}

Our own implementation uses a \texttt{sequential} crew with four agents ---
planner, writer, reviewer, and reference curator --- matching the structure
described in \texttt{docs/PLAN.md}.

\section{LaTeX: A Strong Standard for Technical Publishing}

\LaTeX{} is a document-preparation system known for high-quality typesetting
of scientific and technical material~\cite{lamport1994latex}. Rather than
``what you see is what you get,'' it follows ``what you see is what you
mean'': authors write plain text with markup that defines structure,
formatting, cross-references, citations, equations, and figures, and a
compiler produces a typeset PDF. Its advantages include professional output,
structural consistency, automatic numbering of sections, figures, and
references, version-control-friendly plain-text sources, and a clean
separation of content from style. The trade-off is the learning curve and the
need to debug compilation errors --- which is exactly what makes it an
attractive target for assisted generation.

\section{Generative AI Approaches to Document Creation}

Many existing approaches use a single LLM to generate outlines, summaries, or
whole articles, often with prompt engineering, retrieval-augmented
generation, or fine-tuning. These methods produce coherent prose but struggle
with highly structured, technically precise output: maintaining complex
hierarchy and cross-references, generating compilable \LaTeX{} syntax,
keeping style consistent across a long document, and integrating external
tools. Distributing the work across specialised agents --- with dedicated
steps for planning, writing, reviewing, and references --- is our attempt to
get more control than a single pass would give. This matches what agent
benchmarks such as AgentBench report: even strong LLMs remain unreliable on
long multi-step agentic tasks, which is exactly where explicit task structure
helps~\cite{agentbench2023}.
