% 05_poc_to_production.tex — converted from content/book.md, "5. From PoC to
% Production" (Stage 9.3).

\chapter{From PoC to Production}

\section{Iterative Development and Refinement}

Moving from a basic proof-of-concept to something more reliable is iterative.
Early on, the focus is on getting the crew to run end-to-end at all. Later
iterations involve refining the prompts so the content stays on-topic,
improving how agents pass context to one another, adding error handling, and
testing on larger inputs. In this project the iteration was visible and
honest: an early full run produced off-topic, placeholder-filled content and
was kept only as diagnostic evidence; after the prompts and metadata binding
were hardened, a later run produced on-topic candidate content that this very
document is derived from.

\section{Deployment Considerations}

A production deployment would need to address infrastructure (cloud or
on-premise compute), secret management (API keys read from environment
variables or a secrets manager, never embedded in code), model selection
(balancing cost and quality), and scalability (containers, task queues, and
sensible resource limits). These are design considerations we have thought
through rather than a deployment we have already operated at scale.

\section{Monitoring, Maintenance, and CI/CD}

A maintainable version of the pipeline would log every agent interaction,
track runtime and token usage per run, alert on repeated failures, and
periodically sample output quality. Maintenance includes re-checking the
chosen model as versions change, keeping tool and dependency versions
current, and feeding human feedback back into the prompts. Continuous
integration would run the offline test suite and linters on every commit
before any change is deployed --- which is the workflow this project already
follows for its own code.
